Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2023-10-26 README.Rmd
revert to simple README for now

---
title: ""
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
always_allow_html: true
---

```{r setup, include=F, echo=F}
library(tidyverse)
devtools::load_all("D:/repositories/projectlog")
#source('scripts/dependencies.R')
knitr::opts_chunk$set(echo = F, message = F, warning = F)

```
<br>
This repository contains data, code, and output for a project entitled "Working memory performance in adverse environments: Enhanced, impaired, or intact?". A Stage 1 snapshot of the project has been submitted to [Peer Community in Registered Reports (PCI-RR)](https://rr.peercommunityin.org/)

# Project History

Below is an overview of all the major milestones of this project, including a description and links.
The links take you to the historic version of the project that corresponds to the milestone.

```{r}
proj_history <-
  gert::git_tag_list() |>
  dplyr::rename(
    milestone = name,
    milestone_hash = commit) |>
  mutate(
    commit_hash = (\(x) purrr::pmap_chr(list(milestone, ref, milestone_hash), .f = function(milestone, ref, milestone_hash) {
      gert::git_commit_info(milestone_hash)$id
    }))()
  ) |>
  left_join(
    gert::git_log() |>
      rename(commit_hash = commit)
  ) |>
  mutate(
    milestone_link = paste0(get_git_url(), '/releases/tag/', milestone),
    link = commit_hash,
    commit_link = paste0(get_git_url(), '/tree/', commit_hash)
  )

reactable::reactable(
  proj_history |> select(milestone, timestamp = time, author, message, link),
  columns = list(
    milestone = reactable::colDef(html = TRUE, cell = function(value, index) {
      sprintf("<a href='%s' target='_blank'>%s</a>", proj_history$milestone_link[index], value)
    }),
    link = reactable::colDef(html = TRUE, cell = function(value, index) {
      sprintf("<a href='%s' target=' _blank'>%s</a>", proj_history$commit_link[index], value)
    })
  )
)
```
### Contact

For questions or comments, feel free to contact me at p.c.s.vermeent@gmail.com.

>>>>

---
title: "Working memory performance in adverse environments: Enhanced, impaired, or intact?"
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=F, echo=F}
library(tidyverse)
devtools::load_all("D:/repositories/projectlog")
#source('scripts/dependencies.R')

knitr::opts_chunk$set("ft.shadow" = FALSE, echo = F, message = F, warning = F)

```
<br>
This repository contains data, code, and output for a project entitled "Working memory performance in adverse environments: Enhanced, impaired, or intact?". A Stage 1 snapshot of the project has been submitted to [Peer Community in Registered Reports (PCI-RR)](https://rr.peercommunityin.org/).
